A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-10 main.tex
3.5 wording

In practical applications $\bZ \bgamma$ is unlikely to be entirely orthogonal to population structure. However, the degree to which it reflects population structure \anna{and has the potential to bias SNP-phenotype associations can be inferred from $\bX$ and quantified by \anna{\eqref{eqn:ratio}}. We will use this metric in our analysis of our simulation results in Section \ref{sec:results}. Given the high-dimensional nature of our data, we will approximate $(\bX^\T \bX)^{-1}$ using a low-rank approximation. We use this approach as opposed to that of a generalized inverse in order to ensure a unique solution.}

>>>>

In practical applications $\bZ \bgamma$ is unlikely to be entirely orthogonal to population structure. However, the degree to which it reflects population structure \anna{and has the potential to bias SNP-phenotype associations can be inferred from $\bX$ and quantified by \anna{\eqref{eqn:ratio}}. We will use this metric in our analysis of our simulation results in Section \ref{sec:results}. Given the high-dimensional nature of our data, we use a low-rank approximation of $(\bX^\T \bX)^{-1}$. We use this approach as opposed to a generalized inverse in order to ensure a unique solution.}
